---
title: "Individual Days 2014 LST"
author: "Madeline Gorchels"
date: "12/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file is for the coalating of the days from the summer of 2014 to determine the relationship between canopy and lst for summer months. Each of the files is saved as "t_l_Day_Month_Year" or "t_l_18_8_2014". Important data such as the proximity to a rain event of above __ inches percipitation, recorded Austin temperature in Camp mabry during this time, will be recorded for each different datapoint. 

##Loading Packages
```{r}
library(tidyverse)
library(sf)
library(leaflet)
library(tmap)
library(spatstat)
library(maptools)
library(sp)
library(raster)
library(beepr)
library(RColorBrewer)
library(stargazer)
library(Stack)
```

##Reading in the many spatial datasets 
```{r}
august8 = as.data.frame(st_read(dsn = ".", layer = "t_l_18_8_2014") %>%
  st_transform(crs = 4326) %>% 
  filter(Distance_1==0) %>% 
  mutate(lst=grid_cod_1) %>% 
  mutate(lst_F = lst*(9/5)+32) %>% 
  mutate(tree_cover=grid_code/10000) %>% 
  dplyr::select(tree_cover,lst,lst_F))

september3 = as.data.frame(st_read(dsn = ".", layer = "t_l_3_9_2014") %>% #needs to be rejoined
  st_transform(crs = 4326)%>% 
  filter(Distance_1==0) %>% 
  mutate(lst=grid_cod_1) %>%
  mutate(tree_cover=grid_code/10000) %>% 
  dplyr::select(tree_cover,lst))

july14 = as.data.frame(st_read(dsn = ".", layer = "t_l_14_7_2014") %>%
  st_transform(crs = 4326) %>% 
  filter(Distance_1==0) %>% 
  mutate(tree_cover=grid_code/10000) %>% 
  mutate(lst=grid_cod_1/1000) %>% 
  dplyr::select(tree_cover,lst))

may14 = as.data.frame(st_read(dsn = ".", layer = "t_l_14_5_2014") %>%
  st_transform(crs = 4326) %>% 
  filter(Distance_1==0) %>% 
  mutate(tree_cover=grid_code/10000) %>% 
  mutate(lst=grid_cod_1/1000) %>% 
  dplyr::select(tree_cover,lst))

```
##Merging the datasets

```{r}
summer_lst=rbind(may14,july14,august8,september3)
```


##Creating a linear model for all days
```{r}
tree_reg_days = lm(lst~tree_cover, data = summer_lst)
summary(tree_reg_days)
```

##Looking at just the hottest day (August 8)
```{r}
tree_reg_aug = lm(lst~tree_cover, data = august8)
summary(tree_reg_aug)
```
```{r}
ggplot(august8)+
  geom_point(aes(x=tree_cover,y=lst_F))+
  theme_classic()+
  #labs(title = "Relationship Between Urban Heat Island and Simulated \nTree Canopy by Austin Census Tract", y = "Comparitive Land Surface Temperature Intensity", x = "Simulated Tree Intensity")+
  geom_smooth(method = "lm", aes(x = tree_cover,y=lst_F))+
  geom_text(x = 0.80, y = 91, aes(label = "*** R Squared = 0.26"))+#+
  #scale_x_continuous(breaks=c(min(tree_lst$tree_cover), max(tree_lst$tree_cover)), labels=c("Low","High")
   scale_x_continuous(expand = c(0,0))+
  ylab("Average Land Surface Temperature (F)")+
  xlab("Fraction Tree Covered")
```



```{r}
3.0*(9/5)
```



