---
title: "UMEP Data Wrangling"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The purpose of this markdown is to wrangle some data downloaded from NOAA to use as an input for the UMEP model. After running UMEP, I'm hoping to generate a SUEWS compatable data set for Austin to test the model.

###Step 1: Loading Packages and Reading in the csvs 
```{r}

library(tidyverse)
library(janitor)
library(lubridate)

```


The merge data set combines the two in a not real, but useful way in excel. This is only for testing the SUEWS model process
```{r}
weather_data = read_csv("AustinJuneExampleWeather.csv")
radiation_data = read_csv("AustinJuneExampleData.csv")
weather_maser = read_csv("AustinJuneExampleDatamerge.csv")
```

###Step 2: Finding a way to convert the two different time signatures
One data set uses five minute intervals for the entire 24 hour period of the day. the other dataset uses measurements twice an hour. Both will serve for UMEP, but require some wrangling to match up. 

```{r}
wm_clean = weather_maser %>% 
  mutate(rainfall=(as.numeric(precipitation_in))*25.4) %>%
  mutate(wind=windspeed_mph*0.44704)%>%
  mutate(pressure = pressure_Hg*3.38639) %>% 
  mutate(radiation = kwm2/1000) %>% 
  select(year, month, day, hour, minute, temp, rh, wind, rainfall, pressure, radiation
         )


write_delim(wm_clean, 
            "austin_june.csv", 
            delim = ",", 
            na = "")
```
###Step 3: Converting the UMEP data into SUEWS format
Reading in the converted data file from the UMEP plugin in QGIS
```{r}
md_UMEP = read.table("W_1999_data_60.txt", header=TRUE, sep= "", dec = ".")

```

A problem with this data set is that there are missing values and this will give an error message. The data needs to be replaced using a linear gapfiller. I found one in a precipitation prediction package. We shall see how this works. 
```{r}
library(hyfo)
#the relevent function is fillGap
```

I need to convert the default filler (9999 to NA so the package can read it)
```{r}
md_filled = md_UMEP %>% 
  case_when(press==9999~"NA")
```

