---
title: "WESimSetUp"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(janitor)
```


I am creating this markdown for wrangling data to input in the WESim model from the Pacific Institute. First is the given data set on the amount of energy each of the water plants used in specific months. 

### Loading the Austin Water Facility Data 
```{r}
austin_plants = read_csv("Austin_WaterEnergy_Consumption_for_All_Plants.csv") %>% 
  clean_names()
austin_plant_water = read_csv("Austin_Water_-_Gallons_of_Water_and_Wastewater_Treated.csv") %>% 
  clean_names()
```


### Joining the data sets of energy and water consumption for the facilities 
```{r}
austin_plant_sum = full_join(austin_plant_water,austin_plants) %>% 
  group_by(plant, year) %>% 
  filter(!is.na(mg_treated)) %>% 
  filter(!is.na(type_of_plant)) %>% 
  summarise(
    meankwr = mean(k_wh_per_mg_treated),
    meanwater = mean(mg_treated)
  )
```

### Loading a data set that has the breakdown of Austin Energy sources 
Renewable breakdown is estimated from: https://austinenergy.com/ae/about/environment/renewable-power-generation

As of June 26, 2019 the renewable energy split was:
644.6 MW Solar (32.7%)
1219 MW Wind (61.8%)
107.8 MW Biomass (5.5%)

For original data from the city of Austin, see the "Austin_Utility_Orginal.csv"

```{r}
austin_energy = read_csv("Austin_Utility_Energy_Renewable_Edits.csv") %>% 
  clean_names()
```



```{r, include=FALSE}
#Calculating the emission factors for the energy sources for Austin using the data from above and the EPA tool https://www.epa.gov/sites/production/files/2015-07/documents/emission-factors_2014.pdf
#for utility coal, 95.52 is kg CO2 per mmBtu, 11 for CH4, 1.6 for NOX
#For biomass (wood based as is the Austin plant) 93.80 7.2 3.6
#Nuclear--not finding anything good for this, going to assume that it is 0. Big assumption
emission_factors = data.frame(fuel = c("coal", "coal", "coal", "biomass", "biomass", "biomass"), gas=c("CO2", "CH4", "NOX", "CO2", "CH4", "NOX"), mmbtu = c(95.52, 0.11, 0.016, 93.80, 0.072, 0.036)) %>% 
  mutate(kwh = round(mmbtu*0.0034095106405145, 6))

```

### Creating a tibble that has both the facilities and their breakdown of energy use
```{r}
austin_energy_sum = full_join(austin_plant_sum,austin_energy) %>% 
  filter(!is.na(plant)) %>%
  filter(!is.na(coal)) %>% 
  mutate(perc_coal = (coal/100)*meankwr) %>% 
  mutate(perc_natural_gas_oil = (natural_gas_oil/100)*meankwr) %>% 
  mutate(perc_nuclear = (nuclear/100)*meankwr) %>% 
  mutate(perc_solar = (solar/100)*meankwr) %>% 
  mutate(perc_wind = (wind/100)*meankwr) %>% 
  mutate(perc_biomass = (biomass/100)*meankwr) %>% 
  select(year, plant, meankwr, meanwater, perc_coal, perc_natural_gas_oil, perc_nuclear, perc_wind, perc_solar, perc_biomass) #%>% 
  #filter(year == 2017)
 
```


### Exporting the energy sum csv that only includes water treatment plants

```{r}
austin_water_treat = austin_energy_sum %>% 
  filter(plant !="SAR Plant") %>% 
  filter(plant != "Walnut Creek Plant") %>% 
  group_by(plant) %>% 
  summarise(mean_coal = mean(perc_coal), 
            mean_ng = mean(perc_natural_gas_oil)*0.0341296, #to convert to therms
            mean_wind = mean(perc_wind), 
            mean_solar = mean(perc_solar), 
            mean_biomass = mean(perc_biomass), 
            mean_nuclear = mean(perc_nuclear), 
            noncarbon_renew = mean_solar+mean_wind+mean_nuclear)


write_delim(austin_water_treat, 
            "austin_water_treatmemt.csv", 
            delim = ",", 
            na = "")
```

